Boutiques: a flexible framework to integrate command-line applications in computing platforms

### 2018-02-02 boutiquespaper.tex
Changed shell to sh

The core component of the descriptor is a command-line template
complying to the syntax of the \texttt{bash} UNIX shell, the default
shell on most of the Linux distributions and on OS X. The command-line
template is a single string that may contain placeholders for input and output values, called
value keys. It may also encompass several commands separated by
\texttt{bash} constructs such as semicolons, pipes (\texttt{|}) or
ampersands (\texttt{\&}), to facilitate the embedding of basic
operations on the command line, for instance directory creation, input
decompression or output archival.

>>>>

The core component of the descriptor is a command-line template
complying to the syntax of the \texttt{sh} UNIX shell, the default
shell on most of the Linux distributions and on OS X. The command-line
template is a single string that may contain placeholders for input and output values, called
value keys. It may also encompass several commands separated by
\texttt{sh} constructs such as semicolons, pipes (\texttt{|}) or
ampersands (\texttt{\&}), to facilitate the embedding of basic
operations on the command line, for instance directory creation, input
decompression or output archival.
